### 2014-06-06 method.tex
method intro is good and adjusted figure 2

We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and for each batch of ROIs, transforms them to canonical size and classifies with a CNN, obtaining multi-class scores.
After all batches have scores, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.

As summarized in \autoref{fig:combined}, we start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
We then select a batch of highly-scoring ROIs and classify them with the CNN -- but the CNN may additionally be sped up with cascaded structure.
After the batch is scored, we optionally re-score the remaining ROIs, and repeat.

For the quick feature, we consider the CNN pixel gradient in \autoref{sec:gradient} and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
The Cascaded CNN is described in \autoref{sec:ccnn}.
The dynamic region selection is explained in \autoref{sec:dynamic}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
\caption{
Dynamic region selection combines both speedups and introduces another.
}\label{fig:combined}
\end{center}
\end{figure}

>>>>

We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs).
ROIs are taken in batches: transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
After all batches have been scored, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.

We start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
We then select a batch of highly-scoring ROIs and classify them with the CNN -- which can additionally be sped up with cascaded structure.
After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until we're either out of time, or out of regions.
\autoref{fig:combined} summarizes the process.

For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions, as described in \autoref{sec:region}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
The Cascaded CNN is described in \autoref{sec:ccnn}.
The region selection is explained in \autoref{sec:dynamic}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
\caption{
Our method scores each region of interest with a fast feature (we evaluate several), allowing us to pick promising regions first.
The regions are classified with the original CNN, or a sped-up Cascade-CNN.
The properties of the regions can play a role in selecting the next batch of regions.
}\label{fig:combined}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Region statistics}\label{sec:region}
